A Statistical Framework to Investigate the Optimality of Neural Networks for Linear Inverse Problems

### 2022-03-12 manuscript/main.tex
Abstract first draft
And small re-structuration
First draft conclusions

\author{Pakshal~Bohra, Pol~{del Aguila Pla},~\IEEEmembership{Member,~IEEE},
Jean-Fran\c{c}ois~Giovannelli, and Michael~Unser,~\IEEEmembership{Fellow,~IEEE}
\thanks{This work was funded by the Swiss National Science Foundation under
Grant 200020\_184646 / 1.}
\thanks{P.~{del Aguila Pla} is with the CIBM Center for Biomedical Imaging,
Switzerland.}
\thanks{P. Bohra, P.~{del Aguila Pla} and M. Unser are with the Biomedical
Imaging Group, \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne, 1015
Lausanne, Switzerland (e-mail: pakshal.bohra@epfl.ch;
pol.delaguilapla@eplf.ch; michael.unser@epfl.ch).}
\thanks{J.F. Giovannelli is with IMS (Univ. Bordeaux, CNRS, B-INP), UMR 5218,
F-33400 Talence, France (e-mail: jean-francois.giovannelli@u-bordeaux.fr).
}}%

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}

\end{abstract}
% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}

\end{IEEEkeywords}

@@

@@

    \input{cibm_ack}

>>>>

\author{Pakshal~Bohra, Pol~{del Aguila Pla},~\IEEEmembership{Member,~IEEE},
Jean-Fran\c{c}ois~Giovannelli, and Michael~Unser,~\IEEEmembership{Fellow,~IEEE}
\thanks{This work was funded by the Swiss National Science Foundation under
Grant 200020\_184646 / 1.}
\thanks{P.~{del Aguila Pla} is with the CIBM Center for Biomedical Imaging,
Switzerland.}
\thanks{P. Bohra, P.~{del Aguila Pla} and M. Unser are with the Biomedical
Imaging Group, \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne, 1015
Lausanne, Switzerland (e-mail: pakshal.bohra@epfl.ch;
pol.delaguilapla@epfl.ch; michael.unser@epfl.ch).}
\thanks{J.F. Giovannelli is with IMS (Univ. Bordeaux, CNRS, B-INP), UMR 5218,
F-33400 Talence, France (e-mail: jean-francois.giovannelli@u-bordeaux.fr).
}}%

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
    \input{secs/abstract}
\end{abstract}
% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
    \input{secs/keywords}
\end{IEEEkeywords}

@@

    \input{secs/conclusion}

@@

    \input{secs/cibm_ack}
